From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-12-09 paper.tex
Mention the face rotation ranges that dlib can handle

Besides being fast, the face alignment algorithm has been found to perform well
in terms of robustness, including in a range of difficult situations
(occlusions, large head rotations) as encountered in field experiments.
Figure~\ref{head_pose_real_world} shows a selection of such difficult scenes
with one child.

>>>>

Besides being fast, the face alignment algorithm has been found to perform well
in terms of robustness, including in a range of difficult situations encountered
in field experiments, like partial occlusions or large head rotations (we have
measured the default {\tt dlib} model to be able to track a face
with rotations up to $\pm 40\degree$
horizontally and $\pm 30\degree$ vertically).
Figure~\ref{head_pose_real_world} shows a selection of such difficult scenes
with one child.
